CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-12-04 codecheck-paper.tex
first version of conclusions

\begin{itemize}
\item
  CODECHECK works! we have created 23 certificates to demonstrate it.
\item 
  CODECHECK and can increase trust in results, underlies the same
  limitations as peer review (needs people with time), but also the same
  power (community, reasoning of human)
\item
  possibility to allow CI for open papers such that for ``nearly free''
  we can find out when softwave breaks, and if provenance tools are
  used, when.
\item
  How to embed this in journals.
\item
  When some journals have it - what are crucial decisions/pain points?
  How open do they make the check itself and its outputs, and how does it
  relate/influence the openness of regular peer review
\item
  When is CODECHECK redundant? will it become part of regular peer
  review? or, if ayuthors become more skillful, then everything becomes
  automated, and no need for codecheck. CODECHECK disappearing is then a
  measure of success.
\item
  codecheck allows innovation independent of finance model of the journal
  and current peer review practices; evolutionary now, the "norm" later
\end{itemize}

@@

\clearpage
\begin{itemize}
\item
  role of data and code, data science
\item
  reproducible resarch
\item
  data enclaves
\item
  CASCAID
\item
  ROpenSci/PyOpenSci (and how their software review differs, though they
  also collaborate with journals,
  \url{https://devguide.ropensci.org/softwarereviewintro.html})
\item
  time capsules \textgreater{}
  \url{https://twitter.com/DougBlank/status/1135904909663068165?s=09}
\item
  science is changing:
  \url{https://theconversation.com/what-you-need-to-know-about-how-coronavirus-is-changing-science-137641}
\item
  reproducibility is important, also

>>>>

CODECHECK works!
We have created a considerable number of certificates to demonstrate it.
The creation of the certificates and the interactions with authors and
editors not only improved the principles and the workflow, but also
confirmed the approach taken. CODECHECKs and can increase trust in
scientific results. Yet, they underly the same limitations as peer review
in general and are closely connected to larger disruptions and challenges
in scholarly communication \cite{eglen_recent_2018,tennant_ten_2019}, 
including the tensions between commercial publishing and reviewer's often
free labour.
Even more, it is clear that establishing CODECHECK-like systems can be 
impeded by and must be seen in connection to much larger issues in 
science, such as broken metrics or malpractices triggered by publication
pressure \cite{piwowar_altmetrics:_2013,nosek_promoting_2015}.
While developed for the current "paper"-centric publication process and
being compatible with different styles of peer review, the CODECHECK 
principles would also work well with novel publication paradigms that enable
much more iterative and granular communication of scientific outputs,
e.g., Octopus \cite{}. An explicit segmentation of research steps could
even make the focus of a CODECHECK, e.g., on the analysis sub-publication,
easier.

If adopted today, a CODECHECK system, even if temporal in a sustainable 
transition towards more open publication and review practices, can contribute
to increased trust in the results of research.
More reproducible practices initiated by CODECHECKs could lead
communities/disciplines to reach a state where authors do provide good
enough material and reviewers have acquired broady enough skills that
the latter will generally conduct a CODECHECK-level of checking, and
only in especially sophisticated cases will a specialised codechecker
be included.
The main challenge for us remains to get journals to embrace the
idea behind CODECHECK, whether they use the name for it or not.
This \emph{cultural change}, however, is needed for the valuation of the
efforts that go into proper evaluation of papers.
With the implementation of CODECHECK workflows, the question of training
codecheckers will become relevant. We expect both a mentoring scheme within
the CODECHECK community (experienced codecheckers provide on the job training
or serve as fallback advisors) as well as collaboration with reproducible
research initiatives such as
ReproHack\footnote{https://reprohack.github.io/reprohack-hq/},
ReproducibiliTea\footnote{https://reproducibilitea.org/}
\cite{fitzgibbon_brewing_2020},
and Repro4Everyone\footnote{https://repro4everyone.org/}
\cite{auer_reproducibility_2020},
to be able to grow the pool of codecheckers as needed.
The initial reaction of the scientific community, where up to today over 
twenty people spontaneously signed up as volunteer codecheckers after talks
on the initiative, makes us feel optimistic that the time is right for 
putting scholarly peer review on the path to facilitate sharing and execution
of computer programs and documenting reproducibility of results.

\begin{itemize}
\item

\item

\item
  possibility to allow CI for open papers such that for ``nearly free''
  we can find out when softwave breaks, and if provenance tools are
  used, when.
\item
  How to embed this in journals.
\item
  When some journals have it - what are crucial decisions/pain points?
  How open do they make the check itself and its outputs, and how does it
  relate/influence the openness of regular peer review
\item
  When is CODECHECK redundant? will it become part of regular peer
  review? or, if ayuthors become more skillful, then everything becomes
  automated, and no need for codecheck. CODECHECK disappearing is then a
  measure of success.
\item
  codecheck allows innovation independent of finance model of the journal
  and current peer review practices; evolutionary now, the "norm" later
\end{itemize}

@@

\clearpage
\begin{itemize}
\item
  The Lancet's statistical review process: areas for improvement by authors
  \url{https://www.thelancet.com/journals/lancet/article/PII0140-6736(92)90409-V/fulltext}
\item
  data enclaves
\item
  CASCAID
\item
  ROpenSci/PyOpenSci (and how their software review differs, though they
  also collaborate with journals,
  \url{https://devguide.ropensci.org/softwarereviewintro.html})
\item
  time capsules \textgreater{}
  \url{https://twitter.com/DougBlank/status/1135904909663068165?s=09}
\item
  science is changing:
  \url{https://theconversation.com/what-you-need-to-know-about-how-coronavirus-is-changing-science-137641}
\item
  reproducibility is important, also
